### 2021-04-13 02_abstract/abstract.tex
Small optimizations of abstract

To reduce uncertainties in \acs{ECS} projected by the \acs{CMIP}6 models, 11
published emergent constraints on \acs{ECS} (mostly derived from models
participating in \acs{CMIP}5, the predecessor generation of \acs{CMIP}6) are
systematically analyzed. Emergent constraints are potentially promising
approaches to reduce uncertainties in climate model projections by combining
observations and output from \acsp{ESM}. The focus of this analysis is on
testing if these emergent constraints hold for \acsp{ESM} participating in
\acs{CMIP}6. Since none of the emergent constraints considered here have been
derived from the \acs{CMIP}6 ensemble, the \acs{CMIP}6 models can be used for
cross-checking the emergent constraints on a new model ensemble. The
application of the emergent constraints to \acs{CMIP}6 data shows a decrease in
skill and statistical significance of the emergent relationship for nearly all
constraints, with this decrease being large in many cases. Consequently, the
size of the constrained \acs{ECS} ranges ($66 \unit{\%}$ confidence intervals)
widens by $51 \unit{\%}$ on average in \acs{CMIP}6 compared to \acs{CMIP}5.
This is likely related to the increased multi-model spread of \acs{ECS} in
\acs{CMIP}6, but may in some cases also be due to spurious statistical
relationships or a too-small number of models in the ensemble that the emergent
constraint was originally derived from. The corresponding best estimates of
\acs{ECS} given by the emergent constraints also increase from \acs{CMIP}5 to
\acs{CMIP}6 by $12 \unit{\%}$ on average. This can at least be partly explained
by the increased number of high-\acs{ECS} models in \acs{CMIP}6 without a
corresponding change in the constraint predictors, suggesting the emergence of
new feedback processes rather than changes in the strength of those previously
dominant. The results support previous studies concluding that emergent
constraints should be based on an independently verifiable physical mechanism
and that process-based emergent constraints on \acs{ECS} should rather be
thought of as constraints for the process or feedback they are actually
targeting.

>>>>

To reduce uncertainties in \acs{ECS} projected by the \acs{CMIP}6 models, 11
published emergent constraints on \acs{ECS} (mostly derived from models
participating in \acs{CMIP}5, the predecessor generation of \acs{CMIP}6) are
systematically analyzed. Emergent constraints are potentially promising
approaches to reduce uncertainties in climate model projections by combining
observations and output from \acsp{ESM}. The focus of this analysis is on
testing if these emergent constraints hold for \acsp{ESM} participating in
\acs{CMIP}6. Since none of the emergent constraints considered here have been
derived from the \acs{CMIP}6 ensemble, the \acs{CMIP}6 models can be used for
cross-checking the emergent constraints on a new model ensemble. The
application of the emergent constraints to \acs{CMIP}6 data shows a decrease in
skill and statistical significance of the emergent relationships for nearly all
constraints, with this decrease being large in many cases. Consequently, the
sizes of the constrained \acs{ECS} ranges ($66 \unit{\%}$ confidence intervals)
widen by $51 \unit{\%}$ on average in \acs{CMIP}6 compared to \acs{CMIP}5. This
is likely related to the increased multi-model spread of \acs{ECS} in
\acs{CMIP}6, but may in some cases also be due to spurious statistical
relationships or a too-small number of models in the ensemble that the emergent
constraint was originally derived from. The corresponding best estimates of
\acs{ECS} given by the emergent constraints also increase from \acs{CMIP}5 to
\acs{CMIP}6 by $12 \unit{\%}$ on average. This can at least be partly explained
by the increased number of high-\acs{ECS} models in \acs{CMIP}6 without a
corresponding change in the constraint predictors, suggesting the emergence of
new feedback processes rather than changes in the strength of those previously
dominant. The results support previous studies concluding that emergent
constraints should be based on an independently verifiable physical mechanism
and that process-based emergent constraints on \acs{ECS} should rather be
thought of as constraints for the process or feedback they are actually
targeting.
